Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
what is 'snap' data

Second, we want to find out how, and how much, CCLMs can be attuned to
the specificity of communities. We test whether 1. the linguistic
models are correlated with a model of community based only on
co-occurence of users between communities and 2. if latent community
classifiers based on the CCLM can accurately identify that a given message
comes from a given community.

To sum up, we propose to test the following hypotheses:
\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity
\item The layer at which the community embedding is taken into account
  in CCLM influences its perplexity.
\item CCLM can be used to recognize communities based on
  latent bayesian classification.
\item The layer at which the community embedding is taken into account
  influences CCLM and its associated latent classifier.
  % \item There is a correlation between community language complexity and recognizability.
  % This is more of a justification for studying the latent classifier than a real "user-facing" hypothesis.
\item The model representation of communities are correlated with
  co-ocurrence of users between communities.
% \item Community stability is correlated with language complexity
\end{hypotheses}

@@

As a quantitative assessment,
we compare the CCLM-learned community embedding with the community embedding from \citet{Kumar2018},
which is based on community membership.

- Description of the snap data (JP)

We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(Figure~\ref{fig:pairwise-comm-sim}).

@@

>>>>

Second, we want to find out how, and how much, CCLMs can be attuned to
the specificity of communities. We test whether 1. the linguistic
models are correlated with a model of community based only on
co-occurence of users between communities and 2. if latent community
classifiers based on the CCLM can accurately identify that a given
message comes from a given community. Additionally, one may
intuitively assume that linguistically poor communities are easier to
recognize: the less linguistic diversity, the more specific the
language become and the easier it is to identify.

To sum up, we propose to test the following hypotheses:
\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity
\item The layer at which the community embedding is taken into account
  in CCLM influences its perplexity.
\item CCLM can be used to recognize communities based on
  latent bayesian classification.
\item The layer at which the community embedding is taken into account
  influences CCLM and its associated latent classifier.
  % This is more of a justification for studying the latent classifier than a real "user-facing" hypothesis.
\item The model representation of communities are correlated with
  co-ocurrence of users between communities.
% \item Community stability is correlated with language complexity
\item Linguistically poor communities are easier to identify than linguistically rich communities.
\end{hypotheses}

\jp{TODO: Outline of the paper.}

@@

As a quantitative assessment, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them from the comment-community co-occurence matrix,
using data which spans January 2014 to April 2017. We refer the reader
to \citet{Kumar2018}\jp{I actually cannot find in their paper what
  they do.} for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether and how much a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data. 
%
We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(Figure~\ref{fig:pairwise-comm-sim}).

@@

\jp{Go through hypotheses again}
